An exact Riemann solver for multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state

### 2019-05-17 Manuscript.tex
2

\documentclass[review]{elsarticle}
\usepackage{amssymb}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{tikz}
%\usetikzlibrary{arrows,shapes}
%\usetikzlibrary{shapes.geometric}
%\usetikzlibrary{arrows.meta}
\usepackage{authblk}
\usepackage{graphics,graphicx}
\usepackage{mathrsfs}
\usepackage{amsmath,bm}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{setspace}
\graphicspath{{picture/}}
\graphicspath{{TikzFig/}}

@@

\title{A multi-material HLLC Riemann solver with both elastic and plastic waves for 1D  elastic-plastic flows}
\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
%\cortext[mycorrespondingauthor]{
%Correspondence to: Junbo Cheng, Institute of Applied Physics and Computational Mathematics, Beijing 100094, China. E-mail: Cheng\_junbo@iapcm.ac.cn}

@@

In this paper, a multi-material elastic-plastic HLLC-type approximate Riemann solver(MHLLCEP) is developed, with the capability of resolving both elastic and plastic waves, to simulate one-dimensional  multi-material elastic-plastic solid problems with the isotropic elastic-plastic model \cite{wilkins1963calculation} and  the von Mises' yielding condition in the framework of the  high-order cell-centered Lagrangian scheme.

Generally, elastic-plastic flows can be mainly simulated in three ways, Eulerian methods \cite{trangenstein1991higher,miller2001high,barton2009exact}, staggered Lagrangian schemes \cite{wilkins1963calculation} and cell-centered Lagrangian schemes \cite{burton2013cell,kluth2010discretization,maire2013nominally,cheng2017third} that  is considered in this paper. Comparing with the staggered Lagrangian scheme, cell-centered Lagrangian  schemes  have many advantages. Firstly, it's no necessary to add  extra artificial viscosity  which  must be used in the staggered Lagrangian schemes; Secondly, it is easy to guarantee the total energy conservation; Besides, it can also be used to simulate the problems with both  hyper-elastic and hypo-elastic models  \cite{burton2013cell,kluth2010discretization,maire2013nominally,cheng2017third}  as a Lagrangian scheme.

%In the  Godunov-type method
For a cell-centered Lagrangian scheme, a core process is to move the node of grids with the speed of fluids
 % and to construct the conservative flux
 by solving a Riemann problem at each cell face. As the Riemann problem contains many physical structures, especially in elastic-plastic flows, such as elastic waves, plastic waves and contact waves
  %or interfaces between different materials
  , the property of the approximate Riemann solver is of great importance in the simulation. Recently, a lot of works have been done in
  this area. For example, Gavrilyuk et al. \cite{gavrilyuk2008modelling} analyzed the structure of the Riemann solution and construct a Riemann solver for the linear elastic system  of hyperbolic non-conservative models for transverse waves, wherein, an extra evolution equation was added in order to make the elastic transformations reversible in the absence of shock waves. Despres \cite{despres2007geometrical} built a shock solution to a non-conservations reversible system of hypo-elasticity models and found that a sonic point is necessary to construct  the compression solution that begins at a constrained compressed state.  Cheng et al.  \cite{cheng2015high} analyzed the wave structures of one-dimensional elastic-plastic flows and developed an effective two-rarefaction approximate Riemann solver with elastic waves (TRRSE) and built a  second-order and  a third-order cell-centered Lagrangian schemes based on the TRRSE, but the TRRSE is a little  expensive as  the iteration method is used.
In \cite{cheng2016harten}, for one-dimensional elastic-plastic flows, Cheng introduced a HLLCE Riemann solver, which is fast and efficient in resolving elastic waves and plastic waves. In the HLLCE,  Cheng evaluated the deviatoric stresses from the following \emph{assumption: a pressure is continuous across the contact wave}. This assumption is valid for pure fluids, but  in  elastic-plastic flows, this assumption may lead to some errors. There are three cases we need  to consider.
\begin{enumerate}
  \item If states in the star regions on both sides of the contact wave are elastic, this assumption does not result in errors;
  \item If both states reach the elastic limit, there are two cases need  to be taken into account:
  \begin{enumerate}
    \item if both  materials in both sides of the interface are same, this assumption does not result in errors either.
    \item if  materials are different, this assumption will result in big errors because the yielding strengths of different materials are different;
  \end{enumerate}
  \item If one state in one side of the interface reaches the elastic limit, but another is  not,  this assumption will  also result in big errors.
\end{enumerate}

%For above considerations,
In this paper, in order to eliminate these errors,
 we want to construct a new HLLC-type Riemann solver for 1D multi-material elastic-plastic flows. In the new solver, both the elastic waves and plastic waves are correctly resolved and the assumption in \cite{cheng2016harten} that the pressure is continuous across the interface is deleted; Correspondingly, the errors introduced by the assumption will also be eliminated.

Based on the MHLLCEP, we develop a high-order elastic-plastic cell-centered Lagrangian scheme for one-dimensional multi-material elastic-plastic flows. If we directly use the WENO reconstruction method \cite{liu2018novel} for multi-material elastic-plastic problems,
%With a high-order reconstruction scheme,
the spacial stencil may cross the material interface
% and in a multi-material state, and  will cause oscillation
 and numerical oscillations may be caused near the interface. In order to delete the numerical oscillations neat the material interface, a ghost cell method is used
   %in the  multi-material system to obtain a stable high-order reconstruction.
   Combined with an improved third-order WENO scheme\cite{liu2018novel} and the third-order Runge-Kutta scheme, a high-order cell-centered Lagrangian scheme is given in this paper for one-dimensional multi-material elastic-plastic flows.

This paper is organized as follows. In section 2, we briefly introduce the governing equations to be studied. In section 3, the MHLLCEP method is constructed.  Then, high-order elastic-plastic cell-centered Lagrangian scheme is given in section 4. Some numerical examples are presented to validate the method.  Conclusions are shown in section 5.

@@

According to the yielding of the material, the euqations may have different Jacobian matrix and different sonic velocities. We will discuss them seprately.
\subsection{Jacobian matrix in  elastic regions} %and the eigenvalues and eigenvectors}
For the Mie-Gr\"uneisen EOS, if the material is not yielding and 
\begin{equation}
  |s_{xx}| < \frac{2}{3}Y_0,
\end{equation}
the system (\ref{eq:1d}) can be written as
\begin{equation}
 \partial_t \mathbf{Q} +\mathbf{J}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
\end{equation}
where $Q = (\rho, \rho u, \rho E, s_{xx})$, and the Jacobian matrix is 
\begin{equation}\label{eq:Jcb}
  J(Q) = \left[\begin{array}{llll}
      0 & 1 & 0 & 0 \\
      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma & -1 \\
	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u & -\Gamma u^2 -\frac{\sigma}{\rho}+\frac{u^2}{2} +e & (1+\Gamma)u& -u\\
    \frac{4}{3}\mu\frac{u}{\rho} & -\frac{4}{3}\mu\frac{1}{\rho}& 0 & u \\
\end{array}
\right],
\end{equation}
where $\Gamma = \frac{\Gamma_0\rho_0}{\rho} $.

The eigenvalues of the coefficient matrix $\mathbf{J}(\mathbf{Q})$ are given as
\begin{equation}
  \lambda_1 =\lambda_2 = u, \hspace{0.3cm} \lambda_3 = u-c, \hspace{0.3cm} \lambda_4 = u+c,
\end{equation}
where
\begin{equation}\label{eq:c_e}
  \left\{ \begin{aligned}
      & c = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho}},\\
    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
      \end{aligned} \right.
    \end{equation}
The corresponding right eigenvectors are
\begin{equation}\label{eq:eiv}
  r_1 = \left[ \begin{array}{l}
      \frac{1}{b_1} \\
      \frac{u}{b_1} \\
      0 \\
      1 \\
    \end{array}
    \right], \hspace{0.2cm}
    r_2= \left[ \begin{array}{l}
        -\frac{\Gamma}{b_1} \\
        -\frac{\Gamma u}{b_1} \\
        1 \\
        0\\
      \end{array}
    \right], \hspace{0.2cm}
r_3 =   \frac{1}{\phi^2}\left[\begin{array}{l}
        1 \\
        u-c \\
        h -uc \\
        \phi^2
      \end{array}
    \right], \hspace{0.2cm}
r_4 = \frac{1}{\phi^2}\left[\begin{array}{l}
        1 \\
        u+c \\
        h +uc \\
        \phi^2
      \end{array}
    \right],
  \end{equation}
  where
  \begin{equation}
    b_1 = \frac{\partial p}{\partial \rho} - \Gamma E,  \quad h = E +\frac{p-s_{xx}}{\rho},
  \end{equation}
  and
  \begin{equation}
    \phi^2 = a^2 -\frac{\rho_0}{\rho^2} \Gamma_0 s_{xx}-c^2 = -\frac{4\mu}{3}\frac{1}{\rho}.
  \end{equation}
\subsection{Jacobian matrix in  plastic  regions}
When the material is yielding,
\begin{equation}
  |s_{xx}| = \frac{2}{3}Y_0,
\end{equation}
the equations will turn into a more simple system with only constitutive terms as
\begin{equation}
  \partial_t \mathbf{{U}} + \mathbf{J}_p(\mathbf{U})\partial_x \mathbf{{U}}= 0,
\end{equation}
where $\mathbf{U} = (\rho, \rho u, \rho E )$, and the Jacobian matrix is
\begin{equation}
\mathbf{J}_p(\mathbf{U}) = \left[\begin{array}{lll}
      0 & 1 & 0   \\
      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma \\
	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u +\frac{u^2}{2} & -\Gamma u^2 -\frac{\sigma}{\rho} +e & (1+\Gamma)u\\
\end{array}
\right].
\end{equation} 
The eigenvalues of 
The eigenvalues of the coefficient matrix $\mathbf{J}_p(\mathbf{Q})$ are given as
$$\lambda_1 = u,\quad \lambda_2 = u-c, \quad \lambda_3 = u+c,$$
where 
\begin{equation}\label{eq:c_p}
  \left\{ \begin{aligned}
	  & c = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}} ,\\
    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
      \end{aligned} \right.
    \end{equation}
The corresponding right eigenvectors are
\begin{equation}\label{eq:eivp}
  r_1 = \left[ \begin{array}{l}
	  1 \\
	  u \\
	  E-\frac{c^2}{\Gamma}-\frac{\sigma}{\rho}\\
  \end{array}\right], \quad
 r_2 = \left[ \begin{array}{l}
	  1 \\
	  u-c \\
	  E-uc-\frac{\sigma}{\rho}\\
  \end{array}\right], \quad
 r_3 = \left[ \begin{array}{l}
	  1 \\
	  u+c \\
	  E+uc-\frac{\sigma}{\rho}\\
  \end{array}\right].
\end{equation}
Take a comparason  of Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}), we notice that the sonic speed is not continuous between the states of elastic and plastic. This is very important and may cause wrong results if ignoring it.

\subsection{Formulations across the contact wave}\label{sec:contact}
  For  a  system without molecular diffusion, there is no materials convecting  across the contact wave or interface, so the velocities on two sides of  the discontinuity are always equal. % .
  This can also be verified by the eigenvectors  in Eq.(\ref{eq:eiv}) and  Eq.(\ref{eq:eivp}).

@@

According to  the eigenvectors in  Eq.(\ref{eq:eiv}), for the $\lambda_{1}$-wave and $\lambda_{2}$ wave,  we
have
\begin{equation}   \label{e23a}
\frac{d \rho}{1} = \frac{d \rho u}{u}.
\end{equation}
From the above equations, we can easily deduce that
\begin{equation}   \label{e23b}
du = 0,
\end{equation}

Samilarly, using the eigenvectors in Eq.(\ref{eq:eivp}), for the $\lambda_{1}$-wave, we have 
\begin{equation}  
  \frac{d \rho}{1} = \frac{d \rho u}{u},
\end{equation}
we also can get 
\begin{equation}  
du = 0,
\end{equation}
 which means
\begin{equation}   \label{e23c}
  u_{L}^{\ast}=u_{R}^{\ast},
\end{equation}
For convenience, we define
\begin{equation}\label{eq:contact}
  s^* = u_L^* = u_R^*. % \hspace{0.3cm} \sigma_L^* = \sigma_R^*,
\end{equation}
where $s^*$ denotes the velocity of the contact wave.

Then using  the  conservation relations between the contact  wave
\begin{equation}\label{eq:RH11}
	\bm{F}_R^* = \bm{F}_L^*+s^*(\bm{U}_R^*-\bm{U}_L^*),
\end{equation}

From the momentum term in Eq.(\ref{eq:RH11}),
\begin{equation}
  \rho_R^* u_R^{*2}-\sigma^*_R=\rho_L^* u_L^{*2}-\sigma_L^*+s^*(\rho_R^* u_R^*-\rho_L^* u_L^*).
\end{equation}
and taking  $ s^* = u_L^* = u_R^*$ in, we can get the relation of Cauchy stress
\begin{equation} 
  \sigma^*_L = \sigma^*_R,
\end{equation}
is always satisfied.

\subsection{A relation between $\rho$ and $s_{xx}$ in 1D elastic-plastic  equation system}

  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
%  We can get a relation of density and deviatoric stress,
  \begin{equation}
    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
\end{equation}
Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
\begin{equation}\label{eq:rhosxx}
  s_{xx2}=-\frac{4}{3}\mu\text{ln}(\frac{\rho_{2}}{\rho_{1}})+s_{xx1}.
\end{equation}
The subscripts $2$ and $1$ mean the states in front of and behind the wave, respectively.
This relation always hold if there is no yielding in the integration path.
\subsection{Relations across rarefaction waves}\label{sec:rarefaction}
A Rarefaction wave contains a continuous of waves with the speed of $u\pm c$. Now we consider a left-going rarefaction wave as shown in Fig.\ref{fig:Rare} as an example, the state in front of the wave is known as  $(\rho_1,u_1,p_1,s_{xx1})$ and after the wave the state changes to $(\rho_2,u_2,p_2,s_{xx2})$ which is unknown.

\subsection{Relations across  shock waves}\label{sec:shock}
Now we consider a shock wave with a speed of $s$, suppose the state in front of the shock is known as $(\rho_1,u_1,p_1,s_{xx1})$ and the state after the shock is unknown as $(\rho_2,u_2,p_2,s_{xx2})$.

@@

There are mainly three parts in the soluting process.

Firstly, a pre-evaluation need to  be done to detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases. This is done in Section (\ref{sec:eva}) with shock-contact-shock waves assumption.

Secondly,  we solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ in cases (a,b,d,e) in Section \ref{sec:one} and in cases (c,f) in Section \ref{sec:two}.

>>>>

\documentclass[review]{elsarticle}
\usepackage{amssymb}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{tikz}
%\usetikzlibrary{arrows,shapes}
%\usetikzlibrary{shapes.geometric}
%\usetikzlibrary{arrows.meta}
\usepackage{authblk}
\usepackage{graphics,graphicx}
\usepackage{mathrsfs}
\usepackage{amsmath,bm}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{setspace}
\graphicspath{{picture/}}
\graphicspath{{TikzFig/}}
\usepackage{hyperref}

@@

\title{An exact Riemann solver for  multi-material   elastic-plastic flows with Mie-Gr\"uneisen equation of state}
\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
%\cortext[mycorrespondingauthor]{
%Correspondence to: Junbo Cheng, Institute of Applied Physics and Computational Mathematics, Beijing 100094, China. E-mail: Cheng\_junbo@iapcm.ac.cn}

@@

In this paper, an exact  Riemann solver is built with the consideration of both elastic and plastic waves, for one-dimensional  multi-material elastic-plastic materials with the Mie-Gr\"uneisen EOS, isotropic elastic-plastic model \cite{wilkins1963calculation} and  the von Mises' yielding condition.

The  elastic-plastic flow  is  used to describe the deformation process of solid materials under strong dynamics loading, such as explosive or high-speed impact. The simulation of elastic-plastic flows has important application backgrounds, espially in the Implosion Dynamics weapon and Innertial Confine Fusion (ICF). The first try of simulating the elastic-plastic flows was given by  Wilkins \cite{wilkins1963calculation} in 1960s.

Although the control equations of elastic-plastic flow is samilar to the equations in computational fluid dynamics (CFD). But there are mainly three difficulties  of constructing  Riemann solvers in elastic-plastic flows.  Firstly, the constitutive models used in elastic-plastic flows are more complicated. Secondly, the EOS for solid materials are also with more characters. Finally, the yielding process of materials may lead to more wave structures.

Recently, a lot of works have been done in constructing  approximate Riemann solvers for elastic-plastic flows with the considering of structures in the Riemann problem.  For example, Gavrilyuk et al. \cite{gavrilyuk2008modelling} analyzed the structure of the Riemann solution and constructed a Riemann solver for the linear elastic system  of hyperbolic non-conservative models for transverse waves.   Cheng et al. \cite{cheng2015high} analyzed the wave structures of one-dimensional elastic-plastic flows and developed an effective two-rarefaction approximate Riemann solver with elastic waves (TRRSE). 
In \cite{cheng2016harten}, for one-dimensional elastic-plastic flows, Cheng introduced a HLLCE Riemann solver, which is fast and efficient in resolving elastic waves and plastic waves. Then in \cite{liumulti}, Liu et.al remove the unreasonable assumution in HLLCE  which may cause big error in solving  multi-material problems and construct a multi-material HLLC elastic-plastic (MHLLCEP) solver.

As we know, in hydrodynamic  numerical system, the exact Riemann solver is developed before approximate Riemann solvers \cite{godunov1959difference}, and it gives a guide and reference to the development of approximate solvers. However, in the elastic-plastic flows, for its complexity, there are only a few works have been done in constructing the exact Riemann solver. For example, 
Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.  Miller \cite{miller2004iterative} presented a generial iterative method for the solution of the Riemann problem for hyperbolic elastic systems. Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states. As many as thirty-six \cite{gao20171d} and sixty-four \cite{gao2018complete} different solution types are considered in their works.
However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state. This symplification can truely deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.

In this paper, we want to construct an exact Riemann solver for the elastic-plastic equations system with the  isotropic elastic-plastic model and the  von Mises' yielding condition. In this system, the Mie-Gr\"uneisen EOS is used for both the elastic state and plastic state of the material, which is an adequate approximation to a wide variety of materials of interest, includes some gaseous or solid explosives and solid metals under high pressure \ref{ shyue2001fluid}.  According to both the theoretical analyzation and numerical tests \cite{xiao1996numerical}, in this system, there may be three to five waves, including one contact wave and elastic wave (shock or rarefaction wave) or plastic wave or both the elastic and plastic waves in each side of the contact wave. We will prove this, the elastic wave always faster than the pastic wave in one side, so varing with the initial condition, there are $6\times 6$ thirty-six possible cases of the structures in the solution. For a given case, we will obtain theoretical relations of all the states as functions of density. At last,  through an iteration process of densities at both sides of the contact wave, the  exact solution will be obtained. Also, the half Riemann problem and its exact solution are considered in this paper.

This paper is organized as follows. In section 2, we introduce the governing equations to be studied. In section 3, the Riemann problem and the relations for every wave type (contact wave, shock wave and rarefaction wave) is derived.  Then,  the exact Riemann solver  is given in section 4. The half Riemann problem and its solver is introduced in section 5.  Some numerical examples are presented to validate the method in section 6.  Conclusions are shown in section 7.

@@

According to the yielding of the material, the euqations may have different Jacobian matrix and different sonic velocities. We will discuss them seprately.
\subsection{Elastic state}
\subsubsection{Jacobian matrix in elastic regions} %and the eigenvalues and eigenvectors}
For the Mie-Gr\"uneisen EOS, if the material is not yielding and 
\begin{equation}
  |s_{xx}| < \frac{2}{3}Y_0,
\end{equation}
the system (\ref{eq:1d}) can be written as
\begin{equation}
 \partial_t \mathbf{Q} +\mathbf{J}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
\end{equation}
where $Q = (\rho, \rho u, \rho E, s_{xx})$, and the Jacobian matrix is 
\begin{equation}\label{eq:Jcb}
  J(Q) = \left[\begin{array}{llll}
      0 & 1 & 0 & 0 \\
      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma & -1 \\
	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u & -\Gamma u^2 -\frac{\sigma}{\rho}+\frac{u^2}{2} +e & (1+\Gamma)u& -u\\
    \frac{4}{3}\mu\frac{u}{\rho} & -\frac{4}{3}\mu\frac{1}{\rho}& 0 & u \\
\end{array}
\right],
\end{equation}
where $\Gamma = \frac{\Gamma_0\rho_0}{\rho} $.

The eigenvalues of the coefficient matrix $\mathbf{J}(\mathbf{Q})$ are given as
\begin{equation}
  \lambda_1 =\lambda_2 = u, \hspace{0.3cm} \lambda_3 = u-c, \hspace{0.3cm} \lambda_4 = u+c,
\end{equation}
where
\begin{equation}\label{eq:c_e}
  \left\{ \begin{aligned}
      & c_e = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho}},\\
    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
      \end{aligned} \right.
    \end{equation}
The corresponding right eigenvectors are
\begin{equation}\label{eq:eiv}
  r_1 = \left[ \begin{array}{l}
      \frac{1}{b_1} \\
      \frac{u}{b_1} \\
      0 \\
      1 \\
    \end{array}
    \right], \hspace{0.2cm}
    r_2= \left[ \begin{array}{l}
        -\frac{\Gamma}{b_1} \\
        -\frac{\Gamma u}{b_1} \\
        1 \\
        0\\
      \end{array}
    \right], \hspace{0.2cm}
r_3 =   \frac{1}{\phi^2}\left[\begin{array}{l}
        1 \\
        u-c_e \\
        h -uc_e \\
        \phi^2
      \end{array}
    \right], \hspace{0.2cm}
r_4 = \frac{1}{\phi^2}\left[\begin{array}{l}
        1 \\
        u+c_e \\
        h +uc_e \\
        \phi^2
      \end{array}
    \right],
  \end{equation}
  where
  \begin{equation}
    b_1 = \frac{\partial p}{\partial \rho} - \Gamma E,  \quad h = E +\frac{p-s_{xx}}{\rho},
  \end{equation}
  and
  \begin{equation}
    \phi^2 = a^2 -\frac{\rho_0}{\rho^2} \Gamma_0 s_{xx}-c_e^2 = -\frac{4\mu}{3}\frac{1}{\rho}.
  \end{equation}

\subsubsection{A relation between $\rho$ and $s_{xx}$ }

  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
%  We can get a relation of density and deviatoric stress,
  \begin{equation}
    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
\end{equation}
Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
\begin{equation}\label{eq:rhosxx}
  s_{xx}+\frac{4}{3}\mu\text{ln}(\rho) = \text{constant}
\end{equation}
This relation always hold in the elastic state.

\subsubsection{Relations across the contact wave}\label{sec:contact}
  For  a  system without molecular diffusion, there is no materials convecting  across the contact wave or interface, so the velocities on two sides of  the discontinuity are always equal. % .
  This can also be verified by the eigenvectors  in Eq.(\ref{eq:eiv}) and  Eq.(\ref{eq:eivp}).

@@

Thanks to Eq.(\ref{eq:eiv}), for the $\lambda_{1}$-wave we
have
\begin{equation}   \label{e23a}
\frac{d \rho}{\frac{1}{b_{1}}} = \frac{d \rho u}{\frac{u
}{b_{1}}}=\frac{d \rho E}{0} = \frac{d s_{xx}}{1}.
\end{equation}
From the above equations, we can easily deduce that
\begin{equation}   \label{e23b}
du = 0, \quad d(s_{xx}-p)=0,
\end{equation}
 which means
\begin{equation}   \label{e23c}
  u_{L}^{\ast}=u_{R}^{\ast},
\end{equation}
and
\begin{equation}   \label{e23d}
\sigma_{x,L}^{\ast}=\sigma_{x,R}^{\ast},
\end{equation}
where $()_{L}^{\ast}$ and $()_{R}^{\ast}$ denote $()$ in the region
of $\mathbf{W}_{L}^{\ast}$ and $\mathbf{W}_{R}^{\ast}$,
respectively. Here we do not show the details of the derivation for a simple
 presentation.

Similarly, for the $\lambda_{2}$-wave one
has
\begin{equation}   \label{e24a}
\frac{d \rho}{\frac{-\Gamma}{b_{1}}} = \frac{d \rho u}{\frac{-u
\Gamma}{b_{1}}}=\frac{d \rho E}{1} = \frac{d s_{xx}}{0}.
\end{equation}
From the above equations, we can easily deduce  that
\begin{equation}   \label{e24b}
du = 0, \quad dp=0, \quad ds_{xx}=0,
\end{equation}
 which means
\begin{equation}   \label{e24c}
  u_{L}^{\ast}=u_{R}^{\ast},
\end{equation}
\begin{equation}   \label{e24d}
p_{L}^{\ast}=p_{R}^{\ast}, \quad
  s_{xx,L}^{\ast}=s_{xx,R}^{\ast}.
\end{equation}

%where $()_{L}^{\ast}$ and $()_{R}^{\ast}$ denote $()$ in the region
%of $\mathbf{W}_{L}^{\ast}$ and $\mathbf{W}_{R}^{\ast}$,
%respectively.

From  Eq.(\ref{e24d}), we  get that
\begin{equation}   \label{e27a}
\sigma_{x,L} ^{\ast}=  \sigma_{x,R} ^{\ast}.
\end{equation}

At last, for the $\lambda_{1}$ and $\lambda_{2}$ waves, one can find
that the following two relations always hold:
\begin{equation}   \label{e28}
u_{L}^{\ast}=u_{R}^{\ast}, \quad
\sigma_{x,L}^{\ast}=\sigma_{x,R}^{\ast}.
\end{equation}
For convenience, we define
\begin{equation}\label{eq:contact}
  s^* = u_L^* = u_R^*. % \hspace{0.3cm} \sigma_L^* = \sigma_R^*,
\end{equation}
where $s^*$ denotes the velocity of the contact wave.

\subsubsection{Relations across rarefaction waves}\label{sec:rarefaction}
%as an example, the state in front of the wave is known as  $(\rho_1,u_1,p_1,s_{xx1})$ and after the wave the state changes to $(\rho_2,u_2,p_2,s_{xx2})$ which is unknown.

\emph{\textbf{Left-going rarefaction wave} }
Across the left wave associated with $\lambda_3$-wave, ($\lambda_3=u-c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u-c_e} = \frac{d(\rho E)}{h-uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
\end{equation}
which lead to 
\begin{align}
  \label{eq:urho}
  & \text{d} u =-\frac{c_e}{\rho}\text{d}\rho,\\
 \label{eq:Erho}
  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
\label{eq:sxxrho}
& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
\end{align}
Take the relation of EOS (\ref{eq:mie}) in, we can get the pressure  as
\begin{equation}
  dp =  \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
\end{equation}
it can be written as a differential equation of $p(\rho)$
\begin{equation}
  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho),
\end{equation}
where 
\begin{equation}
  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
\end{equation}
The pressure can be solved out as 
\begin{equation}\label{eq:p_rho}
  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
\end{equation}
Then for a given density $\rho$, we can get  the sonic speed $c_e$  and velocity 
\begin{equation}
  u+\int\frac{c_e}{\rho} d\rho = \text{constant}.
\end{equation}

\emph{\textbf{Right-going rarefaction wave} }
Across the right wave associated with $\lambda_4$-wave, ($\lambda_3=u+c_e$), we have
\begin{equation}
  \frac{d\rho}{1} = \frac{d(\rho u)}{u+c_e} = \frac{d(\rho E)}{h+uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
\end{equation}
which lead to 
\begin{align}
  \label{eq:urho}
  & \text{d} u =\frac{c_e}{\rho}\text{d}\rho,\\
 \label{eq:Erho}
  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
\label{eq:sxxrho}
& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
\end{align}
We can get  similar  relations  as the left-going wave as
\begin{equation}
  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
\end{equation}
\begin{equation}
  u-\int\frac{c_e}{\rho} d\rho = \text{constant}.
\end{equation}

\subsubsection{Relations across  shock waves}\label{sec:shock}
Now we consider a shock wave with a speed of $s$, suppose the state in front of the shock is known as $(\rho_1,u_1,p_1,s_{xx1})$ and the state after the shock is unknown as $(\rho_2,u_2,p_2,s_{xx2})$.

@@

There are mainly five  steps in the soluting process. 
\begin{enumerate}
  \item In section (\ref{sec:eva}), a pre-evaluation is done with a shock-contact-shock waves assumption to give an initial values of $\rho^*_L$ and $\rho^*_R$.

  \item  With  given $\rho^*_L$ and $\rho^*^_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.

  \item  We solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ for  different cases in section \ref{sec:one}.

\item At last,   with  the informations in Section \ref{sec:contact},  
\begin{equation}\label{eq:fus}
  \begin{aligned}
	f_u(\rho^*_L,\rho^*_R) = u_L^* -u_R^* = 0,\\
	f_\sigma(\rho^*_L,\rho^*_R) = \sigma_L^* -\sigma_R^* = 0,
\end{aligned}
\end{equation}
 use a Newton iteration method to  get new $\rho^*_L$ and $\rho^*_R$, then do steps 2-5 again until the result convergents. this process is given in Section \ref{sec:iteration}.
\end{enumerate}
\subsection{Pre-evaluation and case classfication}\label{sec:eva}
At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}. According to the conservation relations across the shocks, we have    
\begin{equation}
  \left\{
  \begin{aligned}
	\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
	\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
  \end{aligned}
\right.
\end{equation}
and
\begin{equation}
  \left\{
  \begin{aligned}
	\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
	\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
  \end{aligned}
\right.
\end{equation}
\begin{figure}
  \centering
  \includegraphics[width=8cm]{Tikz-figure7.eps}
  \caption{Pre-evaluation with a three-waves structure.}
  \label{fig:HLLC}
\end{figure}
